---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# wktmo

The goal of wktmo is to convert weekly data to monthly data. Three week formats are accepted: ISO week, epi week and calendar date.

## Installation

You can install wktmo from CRAN with:

```{r gh-installation, eval = FALSE}
install.packages("wktmo")
```

## Example

This is a basic example which shows you how to convert real-world weekly data to monthly data. `weeklyFlu` is a dataset containing weekly influenza cases, including influenza A, influenza B and influenza A+B, in 18 countries during 2010-2015; data are from FluNet, a global web-based tool for influenza virological surveillance. Refer to `help(weeklyFlu)` for more information.

```{r example, echo=TRUE, results='asis'}
library(wktmo)
# extract data
data(weeklyFlu)
#'subset data of interest, e.g. to convert weekly influenza A cases in China
weeklyData <- weeklyFlu$fluA[weeklyFlu$country == "China"]
# convert weekly data to monthly data;
# these two input methods below will return the same results.
# input 1: the start year and wkIndex
monthlyData <- weekToMonth(weeklyData, year = 2010, wkIndex = 1, wkMethod = "ISO")
```
```{r input 1, echo=FALSE}
# display only first ten row of the results
knitr::kable(monthlyData[1:10,])
```
```{r input 2, echo=TRUE}
# input 2: the start date, same results
monthlyData <- weekToMonth(weeklyData, datStart = "04-01-2010", wkMethod = "startDat")
```
```{r input 2r, echo=FALSE}
knitr::kable(monthlyData[1:10,])
```

## Updates

### wktmo 1.0.3

#### Major Changes

Add a real-world dataset, `weeklyFlu`.

Replace examples with new examples using data in `weeklyFlu`.

### wktmo 1.0.2

#### Minor Changes

Improvement on formmatting of examples.

### wktmo 1.0.1

First published on CRAN.

#### Minor Changes

Revisions of DESCRIPTION file.

### wktmo 1.0.0

First submission to CRAN.
